\section{Motivation} \label{sec:intro_motivation}

Eye tracking hardware has been available for a very long time. Studies dating as far back as the 80s show the use of eye trackers in conjunction with computer hardware with accuracies up to about 1/2 degree of visual angle (\cite{colin1986}). Even before cameras and computers were advanced enough to measure anything accurately, mirrors have been used in conjunction with reading excercises to classify saccades and fixations (\cite{vanGog2013}). Current state of the art eye trackers provide massive improvements in accuracy, as well sampling frequency, data quality, data stability and overall ease of use.

Most eye trackers in wide adoption today, are used by researchers for research purposes, with data quality and price tags to match that of large research budgets. As an effect, manufacturers have had limited incentives to promote the commercial availability of the hardware and its accompanying software. Only recently have we seen emerging eye trackers with price tags below thousands of dollars. This enables their use for even the casual gamer, which in turn has remodelled the commercial approach to eye tracking applications.

Traditionally, the leading value proposition for eye tracking hardware has been as an assistive technology for people with disabilities, offering an improvement to the autonomy and quality of life for those in need of alternate input devices (\cite{barry1994}, \cite{corno2002}), but this trend is changing. More recently, the video-game industry has caught wind of the technology, through a series of very promising studies over the past decades (\cite{leyba2004}, \cite{smith2006}, \cite{tobii2017}). What these studies suggest is that eye tracking hardware need not directly substitute existing control input devices, but could rather serve to complement them. For example, game developers can make game graphics more immersive by letting the user's gaze point determine camera focus, depth of field or light exposure. Game characters may interact differently with the user depending on whether the user is maintaining eye contact and so on. All in all, eye tracking provides a more challenging and immersive experience for the user (\cite{antunes2018}), and it's adoption is only going to increase as the technology and its applications advances in the near future.

Another exciting use case for eye tracking is driven by the ever expanding competitive gaming environment. As the video game industry is already worth more than the music and movie industries combined (\cite{mangeloja2019}), all estimates show a positive trend in the interest for \textit{Electronic sports} (eSports). In fact, market reports show that the eSports audience reached 474 million people million in 2018, with a year-on-year growth of +8,7\% (\cite{newzoo2021}). With this impressive growth comes the ever-increasing demand for competitive performance analytics. 

There is always an incentive to be better at whatever game one is playing, especially if the competitive scene is attractive. Naturally the most effective method of improving performance is through direct feedback. Many amateur and pro players tend to subscribe to software services that provide targeted match feedback, as is evident by the success of companies such as Mobalytics and Shadow Esports. At Osiris Performance Analytics AS, we aim to complement existing targeted match feedback with that which can be inferred from eye tracking data analysis.

The analytic potential of eye tracking data is monumental, a potential that exhibits performance enhancing effects on simple learning tasks. The field of psychology amount to years of research on how eye movements and pupil sizes relate to complex cognitive processes (\cite{may1990}, \cite{kahneman1966}). As Tamara Van Gog, professor of educational sciences at the department of education at Utrecht University states, "Eye tracking is not only a useful tool to study cognitive processes and cognitive load in computer-based learning environments but can also be used indirectly or directly in the design of components of such environments to enhance cognitive processes and foster learning." (\cite{vanGog2013}). In a report, she refers to several studies where eye tracking implementations have led to an increase in successful problem solving. Such implementations are outside the scope of this thesis, however they serve as a motivational end to which further research may seek inspiration.
